Determining the alternatives for scalar implicature

### 2016-01-27 Paper/Paper.Rmd
fixed xtable plotting

names(tableCors) <- c("r", "model", "Experiment")
tableCors <- tableCors[c(1, 3, 2),]
tab <- xtable(tableCors)
print(tab, type="latex")

>>>>

names(tableCors) <- c("Model", "Exp. 3a", "Exp 3b")
tableCors <- tableCors[c(1, 3, 2),]
tab <- xtable(tableCors, caption = "Model fit measured by correlation coefficients")
print(tab, type="latex", floating = TRUE, include.rownames = FALSE, comment = FALSE)

### 2016-01-27 Paper/Paper.tex
fixed xtable plotting

Figure \ref{fig:stimuli_exp1}, left, shows the experimental setup.
Participants were presented with a target scalar item and a star rating
(1--5 stars) and asked to judge the compatibility of the scalar item and
star rating. Compatibility was assessed through a binary ``yes/no''
response to a question of the form ``Do you think that the person
thought the food was \_\_\_\_?" where a target scalar was presented in
the blank. Each participant saw all scalar item and star rating
combinations for their particular condition (see Figure
\ref{fig:allScalesTable}), in a random oder.

The two-alternatives condition included only the scalar pairs from Tiel
(2014). The four-alternatives condition included the two scalar items
plus the top two alternatives generated for each scalar family by
participants in Experiment 2. The five-alternatives condition included
the four previous items plus one more ``neutral'' item chosen from those
alternatives generated in Experiment 2. See Figure 1 for the complete
list of alternatives used in each condition.

@@

\caption[Literal listener judgements from Experiments 1a, 3a, and 4]{Literal listener judgements from Experiments 1a, 3a, and 4. Proportion of participants indicating acceptability is shown on the vertical axis, with the horizontal axis showing number of stars on which the utterance was judged. Each line-type shows a different experiment, and colors indicate the different items in the scale (with the experiments including different numbers of items).  Each panel shows one scalar pair.}\label{fig:exp1Plots}
\end{figure*}
\end{CodeChunk}

@@

Figure \ref{fig:exp2_altsPlot_likedLoved} an example alternative set for
the scalar items \emph{liked} and \emph{loved} (combined). Alternative
distributions for the other scalar pairs (e.g.. \emph{good/excellent},
\emph{memorable/unforgettable}) were similarly long-tailed.

@@

@@

\% latex table generated in R 3.2.3 by xtable 1.8-0 package \% Wed Jan
27 09:40:50 2016

\begin{table}[ht]
\centering
\begin{tabular}{rlrr}
  \hline
 & r & model & Experiment \\ 
  \hline
1 & Entailment & 0.54 & 0.57 \\ 
  3 & Top\_two & 0.84 & 0.90 \\ 
  2 & Full & 0.86 & 0.90 \\ 
   \hline
\end{tabular}
\end{table}

>>>>

Figure \ref{fig:stimuli_exp1}, left, shows the experimental setup.
Participants were presented with a target scalar item and a star rating
(1--5 stars) and asked to judge the compatibility of the scalar item and
star rating. Compatibility was assessed through a binary ``yes/no''
response to a question of the form ``Do you think that the person
thought the food was \_\_\_\_?" where a target scalar was presented in
the blank. Each participant saw all scalar item and star rating
combinations for their particular condition, in a random order.

The two-alternatives condition included only the scalar pairs from Tiel
(2014). The four-alternatives condition included the two scalar items
plus the top two alternatives generated for each scalar family by
participants in Experiment 2. The five-alternatives condition included
the four previous items plus one more ``neutral'' item chosen from those
alternatives generated in Experiment 2. See Figure
\ref{fig:allScalesTable} for the complete list of alternatives used in
each condition.

@@

\caption[Literal listener judgements from Experiments 1a,b,c]{Literal listener judgements from Experiments 1a,b,c. Proportion of participants indicating acceptability is shown on the vertical axis, with the horizontal axis showing number of stars on which the utterance was judged. Each line-type shows a different experiment, and colors indicate the different items in the scale (with the experiments including different numbers of items).}\label{fig:exp1Plots}
\end{figure*}
\end{CodeChunk}

@@

Figure \ref{fig:exp2_altsPlot_likedLoved} shows an example alternative
set for the scalar items \emph{liked} and \emph{loved} (combined).
Alternative distributions for the other scalar pairs (e.g..
\emph{good/excellent}, \emph{memorable/unforgettable}) were similarly
long-tailed.

@@

Figure \ref{fig:exp2Plots} plots pragmatic listener judgments
distributions for ``weak'' / ``strong'' scalar pairs (ie
\emph{good}/\emph{excellent}). We only include the original entailment
pairs in this figure for simplicity. Several trends are visible. First,
in each scale participants generated implicatures and were less likely
to assign high star-ratings to weaker scalar terms, despite literal
semantic compatibility. Second, the ``size'' of the difference between
judgments between ``strong'' and ``weak'' scalar items varied by scale,
confirming results found by Tiel (2014).

@@

\begin{table}[ht]
\centering
\begin{tabular}{lrr}
  \hline
Model & Exp. 3a & Exp 3b \\ 
  \hline
Entailment & 0.54 & 0.57 \\ 
  Top\_two & 0.84 & 0.90 \\ 
  Full & 0.86 & 0.90 \\ 
   \hline
\end{tabular}
\caption{Model fit measured by correlation coefficients} 
\end{table}
